Consistency scores in text data

### 2020-08-01 outputs/documents/paper.Rmd
Writing updates. Add one literacture for BERT.

The n-gram models work do not take the linguistic structure of language into account. As @rosenfeld2000two pointed out, "... it may as well be a sequence of arbitrary symbols, with no deep structure, intention or thought behind". The prediction of the next word is only from a few words that are immediately preceding; the context is not taking into account. For this shortcoming, the preditive power of n-gram is largely limited.

@@

[The word representations computed using neural networks are very interesting because the learned vectors explicitly encode many linguistic regularities and patterns. Somewhat surprisingly, many of these patterns can be represented as linear translations. For example, the result of a vector calculation vec("Madrid") - vec("Spain") + vec("France") is closer to vec("Paris") than to any other word vector.]

@@

**Article: word2vec Explained: Deriving Mikolov et al.’s Negative-Sampling Word-Embedding Method**

Developed by Google, Word2Vec is a word embedding model that uses shallow neural network. While it is not a deep learning model, it turns words into a vector representations that deep neural networks can understand. It takes a corpus as its input and output a set of feature vectors that represent the words in the given corpus. @mikolov2013efficient proposed two architectures for learning distributed representations of words within the framework of Word2Vec — Continuous Bag-of-Words Model (CBOW) and Continuous Skip-gram Model. CBOW uses several surrounding words, or the context, to predict a target word. On the other hand, continuous skip-gram takes a single word as input to predict its neighbouring words. For example, consider the sentence "I think therefore I am", a famous quote by Descartes. The focus word is we want to learn the embedding is set to "therefore", and the context window is set to two which will give us the two immediate preceding words and two immediate proceeding words of the focus word. The input for the CBOW is "I, think, I, am" and the output is "therefore". In contrast, the skip-gram model will take "therefore" as the input and out "I, think, I, am" as the prediction.

Word2Vec is trained on the Google News dataset that contains 6 billion tokens and the vocabulary size is restricted to one million most common words (@mikolov2013efficient).

Word2Vec use cases:
1. Find the most similar words (**Keli add example**)
2. Calculate the similarities between a pair of words (**Keli add example**)
3. Find the odd word in a list of words (**Keli add example**)
4. Perform linear algebra to vectorized words. Example:
>  vector("King") - vector("Man") + vector("Woman") = vector("Queen")

**Article: GloVe: Global Vectors for Word Representation**

GloVe stands for global vectors for word representation. It is a pre-trained word embedding model that can capture semantic meanings of words developed by Stanford. 
It is an unsupervised learning algorithm. 
Their disadvantage is that they are context-free and fail to capture higher-level concepts in context.

@@

**Article: Bert: Pre-training of deep bidirectional transformers for language understanding**

This paper is published by researchers at Google AI Language in 2018. The key innovation of BERT is its application of bidirectional training of the Transformer model, which results in a deeper sense of language context and flow.

>>>>

The n-gram models work do not take the linguistic structure of language into account. As @rosenfeld2000two pointed out, "... it may as well be a sequence of arbitrary symbols, with no deep structure, intention or thought behind". The prediction of the next word is only from a few words that are immediately preceding; the context is not taking into account. For this shortcoming, the predictive power of n-gram is largely limited.

@@

@@

Developed by Google, Word2Vec is a word embedding model that uses shallow neural network. While it is not a deep learning model, it turns words into a vector representations that deep neural networks can understand. It takes a corpus as its input and output a set of feature vectors that represent the words in the given corpus. @mikolov2013efficient proposed two architectures for learning distributed representations of words within the framework of Word2Vec — Continuous Bag-of-Words Model (CBOW) and Continuous Skip-gram Model. Both architectures contains three layers: input layer, projection layer and output layer. The input layer encodes words within a context window to one-hot vectors. Using a projection matrix, the input layer is  projected to a projection layer and the features are. Finally, the output layer is a softmax regression classifier that obtains the posterior distribution of words (@rong2014word2vec). The input and output vectors differ in the two architecutres. CBOW uses several surrounding words, or the context, to predict a target word. On the other hand, continuous skip-gram takes a single word as input to predict its neighbouring words. For example, consider the sentence "I think therefore I am", a famous quote by Descartes. The focus word is we want to learn the embedding is set to "therefore", and the context window is set to two which will give us the two immediate preceding words and two immediate proceeding words of the focus word. The input for the CBOW is "I, think, I, am" and the output is "therefore". In contrast, the skip-gram model will take "therefore" as the input and out "I, think, I, am" as the prediction.

Word2Vec is trained on the Google News data set that contains 6 billion tokens and the vocabulary size is restricted to one million most common words (@mikolov2013efficient). The enormous size of data set catches accurate statistical pattern of language and results a comprehensive mapping of word relations to a vector place. The positions of the word vectors reflect their semantic relationships between each other. Therefore, the Word2Vec model performs especially well in word analogy tasks through answering questions such as "$king$ is to $man$ as $queen$ is to __?" @pennington2014glove. The vectorization of words allows the operation of linear algebra for the word vectors in order to get the answer:

>  vector("King") - vector("Man") + vector("Woman") = vector("Queen")

Other Word2Vec use cases:
1. Find the most similar words (**Keli add example**)
2. Calculate the similarities between a pair of words (**Keli add example**)
3. Find the odd word in a list of words (**Keli add example**)

### GloVe

GloVe stands for global vectors for word representation. It is a pre-trained word embedding model that can capture semantic meanings of words developed by Stanford. In the Word2Vec model, the model learn word presentations locally within a context window. On the other hand, GloVe considers the properties of the corpus globally. The benefit of the global approach is that the model can learn about the global statistics of an entire corpus. GloVe can then obtain the co-occurrence probabilities by creating a co-occurrence count matrix for the entire training data set. However, GloVe goes beyond calculating distribution of word by the probability of co-occurrence; it reveals properties of words by the ratio of the probability of co-occurrence of words. For example, consider the two words we want to obtain the word vectors from "ice" and "steam". GloVe reveals their properties by examining their co-occurrence with a variety of probe words, $k$. $K$ can be "solid", which is the property of ice; "gas", which is the property of steam; and "water", which is related to both "ice" and "steam". The ratio of co-occurrence probability is calculated as the following:

> P(k|ice)/P(k|steam)

The ratio between the co-occurrence probability of "ice, solid" pair and "steam, solid" pair is high because the co-occurrence of "ice" and "solid" is higher than the co-occurrence of "steam" and "solid". Reversely, the ratio between the co-occurrence of "ice, gas" pair and "steam, gas" pair is low. Other other hand, the ratio of co-occurrence probability of "ice, water" pair and "steam, water" pair are close to 1 because water is relevant to both "ice" and "steam". Probability alone does not distinguish well relevant words from irrelevant words. For this reason, the researcher of GloVe argued that "the appropriate starting point for word vector learning should be with ratios of co-occurrence probabilities rather than the probabilities themselves (@pennington2014glove)."

@@

BERT stands for Bidirectional Encoder Representations from Transformers (@devlin2018bert). It was released by researchers at Google AI Language in 2018. The key innovation of BERT is its application of bidirectional training of the Transformer model, which results in a deeper sense of language context and flow. What is bidirectional training? In the context of English language, a sentence is constructed from left to right. The context on the left is used to determine the next word on the right. In this sense, GPT models are unidirectional since the probability of the next word is dependent only on the past. It is also possible to reverse the direction and model the sentence from right to left, and BERT incorporates both directions of left-to-right and right-to-left to model bidirectional contexts. BERT uses the bidirectional approach to alleviate by "masked language model" (MLM). The MLM model masks certain words in the input corpus and predict the original words that are masked. The objective is to fuse the representation from the left and right context to enable the pre-training of the deep bidirectional Transformer. For example:

Because BERT employs the Transformer architecture with the self-attention mechanism, fine-tuning is also available.
